---
title: "800-171 Analysis with FR M"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(readr)
library(tidyverse)
library(ggplot2)
library(igraph)
library(dplyr)
```     

    
#800-171 and FedRAMP Moderate Comparison  
  
```{r}
`SP_800_53_Analysis_for_SP_800_171` <- read_excel("~/Documents/GitHub/FedRAMP_SP-800-171_Analysis/SP 800-53 Analysis for SP 800-171.xlsx")
FedRAMP_Master <- read_excel("~/Documents/GitHub/FedRAMP_Baseline_Master/FedRAMP LMH Master.xlsx")

head(SP_800_53_Analysis_for_SP_800_171)
head(FedRAMP_Master)
```

For this analysis, we would want to find the percentage of Security Controls that are within the SP-800-171 and analyze the percentage difference between the two (FedRAMP Moderate and SP-800-171).       
   
```{r}
FedRAMP_Moderate <- FedRAMP_Master %>%
  filter(`FR Moderate` == "Y")

head(FedRAMP_Moderate)
names(FedRAMP_Moderate)
```

      
**Number of Security Control Families in FR M and the SP 800-171.**
```{r}
Count_SCFamilyFRM <- FedRAMP_Moderate %>%
  mutate(total_SCFamilyFRM = length(unique(`Control Family ID`))) %>%
  select(`SC_Family` = `Control Family ID`, 
         total_SCFamilyFRM) %>% 
  distinct()

Count_SCFamilyFRM

Count_SCFamily171 <- SP_800_171_Analysis %>%
  mutate(total_SCFamily171 = length(unique(`800-53 Family`))) %>%
  select(`800-53 Family`, total_SCFamily171) %>%
  distinct() %>%
  rename(`SC_Family` = `800-53 Family`)

Count_SCFamily171

Percentage_SCFamilies <- Count_SCFamilyFRM %>%
  left_join(Count_SCFamily171) %>% 
  mutate(percentage_SCFamilies = total_SCFamily171/total_SCFamilyFRM) %>%
  select(-`SC_Family`) %>%
  distinct()

Percentage_SCFamilies
```
Both, FedRAMP Moderate and SP 800-171 have the same number of Security Control families. This means that SP 800-171 uses the total amount (100%) of possible Security Control family possible.     

  
**Number of Security Control in FR M and the SP 800-171.**
```{r}
Count_SCFRM <- FedRAMP_Moderate %>%
  mutate(total_SCFRM = length(unique(Controls))) %>%
  select(Controls, total_SCFRM) %>%
  distinct()

Count_SCFRM

Count_SC171 <- SP_800_171_Analysis %>%
  mutate(total_SC171 = length(unique(`NIST SP 800-53`))) %>%
  select(`Controls` = `NIST SP 800-53`, 
         total_SC171) %>% 
  distinct()

Count_SC171

Percentage_SC <- Count_SCFRM %>%
  left_join(Count_SC171) %>% 
  mutate(percentage_SC = total_SC171/total_SCFRM) %>%
  select(-`Controls`) %>%
  distinct() %>%
  drop_na()

Percentage_SC
```    
FedRAMP Moderate has a total of 325 Security Controls, while SP 800-171 has 127 of those 415 Security Controls. This means that 39.1% of the Security Controls are in SP 800-171.     
   
    
**Number of Security Control withing each family in SP 800-53 and the SP 800-171.**
```{r}
Count_SCFamily_SCFRM <- FedRAMP_Moderate %>%
  group_by(`Control Family ID`) %>%
  mutate(total_SCFamily_SCFRM = length(`Control Family ID`)) %>%
  select(SC_Family = `Control Family ID`, total_SCFamily_SCFRM) %>%
  distinct()

Count_SCFamily_SCFRM

Count_SCFamily_SC171 <- SP_800_171_Analysis %>%
  group_by(`SR Family`, `800-53 Family`) %>%
  mutate(total_SCFamily_SC171 = length(unique(`NIST SP 800-53`))) %>%
  ungroup() %>%
  group_by(`SR Family`) %>%
  mutate(total_SRFamily_SC171 = length(unique(`NIST SP 800-53`))) %>%
  select(`800-53 Family`, total_SRFamily_SC171, total_SCFamily_SC171) %>%
  distinct() %>%
  rename(`SC_Family` = `800-53 Family`)

Count_SCFamily_SC171

Percentage_SCFamily_SC <- Count_SCFamily_SCFRM %>%
  left_join(Count_SCFamily_SC171, by = "SC_Family") %>% 
  mutate(percentage_SCFamily = total_SCFamily_SC171/total_SCFamily_SCFRM) %>% 
  select(`SR Family`, SC_Family, total_SCFamily_SCFRM, total_SCFamily_SC171, percentage_SCFamily)

Percentage_SCFamily_SC 
```
    
   
##Exporting Data 
    
```{r}
write_csv(`Percentage_SCFamilies`, "Percentage_SCFamilies.csv")
write_csv(`Percentage_SC`, "Percentage_SC.csv")
write_csv(`Percentage_SCFamily_SC`, "Percentage_SCFamily_SC.csv")
``` 